---
title: "Scratch"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---



```{r}
library(tidyverse)
library(DT)
library(tidyquant)
library(quantmod)
library(rvest)
library(rjson)
library(jsonlite)
library(plyr)
library(dplyr)
library(data.table)
```






```{r}
download.file("https://content.ftserussell.com/sites/default/files/support_document/RU2000_MembershipList_20190701.pdf","russell2000list.pdf", mode="wb")
```

```{r}
russell2000<- extract_tables("https://content.ftserussell.com/sites/default/files/support_document/RU2000_MembershipList_20190701.pdf", encoding = "UTF-8",output = "data.frame")
```


```{r}
finstr_test <- xbrl_get_statements(AAPL.BS)
```




```{r}
n <- 0

for(i in russell2000){
  n <- n + 1
  assign(paste0('table',n), rbind(i) %>% select(-3,-6))
}


```

```{r}
rbind(russell2000[[1]]) %>% 
  slice(-1) %>% 
  select(-3,-6)
```

Joel Greenblatt's Magic Formula:

1. Establish a minimum market capitalization (usually greater than $50 million).
2. Exclude utility and financial stocks.
3. Exclude foreign companies (American Depositary Receipts).
4. Determine company's earnings yield = EBIT / enterprise value.
5. Determine company's return on capital = EBIT / (net fixed assets + working capital).
6. Rank all companies above chosen market capitalization by highest earnings yield and highest return on capital (ranked as percentages).
7. Invest in 20–30 highest ranked companies, accumulating 2–3 positions per month over a 12-month period.
8. Re-balance portfolio once per year, selling losers one week before the year-mark and winners one week after the year mark.
9. Continue over a long-term (5–10+ year) period.





```{r}
#Get Russell 3000 index members, represents 98% of all traded US stocks
russell3000 <- tidyquant::tq_index("s&p500")

#Step 1 of Magic Formula is already fulfilled, as the smallest members of the Russell3000 index have market capitalizations of around $200 million (> benchmark 100m)

#Step 2 of Formula: Remove all stocks from the "Financial Services" and "Utilities" sectors
russell3000 <- russell3000 %>%
  dplyr::filter(!grepl("Financial Services", sector), !grepl("Utilities", sector))

#Check that filtering has been done correctly
unique(russell3000$sector)


#Step 3 of formula is already done, as Russell3000 doesn't include ADRs by default

#Step 4: Determine Earning's Yield



```



```{r}

sp500 <- tq_index("s&p500")
```





```{r}

#Release Function
getIncome <- function (ticker, format = "tidy") {
  
  scrape <- function (ticker) {
    repeat {
    tmp<-try({
      yfin_url <- paste0("https://finance.yahoo.com/quote/",ticker,"/financials?p=",ticker)
      page <- read_html(yfin_url)
      nodes <- page %>%html_nodes(".fi-row")
      df = NULL
      
      for(i in nodes){
      r <- list(i %>%html_nodes("[title],[data-test='fin-col']")%>%html_text())
      df <- rbind(df,as.data.frame(matrix(r[[1]], ncol = length(r[[1]]), byrow = TRUE), stringsAsFactors = FALSE))
      }
      
      matches <- str_match_all(page%>%html_node('#Col1-3-Financials-Proxy')%>%html_text(),'\\d{1,2}/\\d{1,2}/\\d{4}')  
      headers <- c('Items','TTM', matches[[1]][,1]) 
      names(df) <- headers
      return(df)
      })
    }
    if (!(inherits(tmp,"try-error"))) 
      break
    }
  

  clean <- function (df) {
    df<- na_if(df,"-")
    df <- df %>%
       mutate_at(2:ncol(df), parse_number)
    
    df[17, 1] <- "Basic EPS"
    df[18, 1] <- "Diluted EPS"
    df[20, 1] <- "Basic W. Average Shares Outstanding"
    df[21, 1] <- "Diluted W. Average Shares Outstanding"
    
    df <- df %>% dplyr::filter(Items != "Operating Expenses" & Items != "Reported EPS"  & Items != "Weighted average shares outstanding")
    return(df)
  }
  
  
  tidy <- function (df) {
    df <- df %>% 
    pivot_longer(c(2:ncol(df)), names_to="date") %>% 
    pivot_wider(names_from = Items)
  
    substrEnd <- function(x, n){
    substr(x, nchar(x)-n+1, nchar(x))
    }
  
    df <- df %>% 
     mutate(ticker=ticker,
            year = substrEnd(date,4))
    
    df <- df %>% 
     select(ticker, date, year, everything())
    
  
    df <- df %>% dplyr::rename(
       "revenue"=`Total Revenue`,
       "cost_revenue" = `Cost of Revenue`,
       "gross_profit" = `Gross Profit`,
       "r&d" = `Research Development`,
       "sg&a" = `Selling General and Administrative`,
       "operating_expenses" = `Total Operating Expenses`,
       "ebit" = `Operating Income or Loss`,
       "interest_expense" = `Interest Expense`,
       "other_income_net" = `Total Other Income/Expenses Net`,
       "ebt" = `Income Before Tax`,
       "tax" = `Income Tax Expense`,
       "income_operations" = `Income from Continuing Operations`,
       "ni" = `Net Income`,
       "ni_to_shareholders" = `Net Income available to common shareholders`,
       "basic_eps" = `Basic EPS`,
       "diluted_eps" = `Diluted EPS`,
       "basic_w_avg_shares" = `Basic W. Average Shares Outstanding`,
       "diluted_w_avg_shares" = `Diluted W. Average Shares Outstanding`,
       "ebitda" = `EBITDA`
    )
    return(df)
  }
  
  
  
  getIncomeRaw <- function(ticker) {
    df <- scrape(ticker)
    return(df)
    #assign(paste0(ticker,"_income_raw"),df,envir = .GlobalEnv)
  }
  
  getIncomeClean <- function(ticker){
    df <- scrape(ticker) %>% 
      clean()
    return(df)
    #assign(paste0(ticker,"_income_clean"),df,envir = .GlobalEnv)
  }  

  getIncomeTidy <- function(ticker) {
    df <- scrape(ticker) %>% 
      clean() %>% 
      tidy()
    return(df)
    #assign(paste0(ticker,"_income"),df,envir = .GlobalEnv)
  }
  
  
  
  ###################
  
  if (format=="tidy") {
    getIncomeTidy(ticker)
  } else if (format=="clean") {
    getIncomeClean(ticker)
  } else if (format=="raw") {
    getIncomeRaw(ticker)
  } else {
    stop('Format can only be "tidy", "clean", or "raw".')
  }
  
}
```




```{r}
getIncome("KO", format="tidy")
```






https://stackoverflow.com/questions/44030983/yahoo-finance-url-not-working

https://query2.finance.yahoo.com/v10/finance/quoteSummary/AAPL?modules=incomeStatementHistory

Yahoo Finance Modules:
modules = [
   'assetProfile',
   'incomeStatementHistory',
   'incomeStatementHistoryQuarterly',
   'balanceSheetHistory',
   'balanceSheetHistoryQuarterly',
   'cashflowStatementHistory',
   'cashflowStatementHistoryQuarterly',
   'defaultKeyStatistics',
   'financialData',
   'calendarEvents',
   'secFilings',
   'recommendationTrend',
   'upgradeDowngradeHistory',
   'institutionOwnership',
   'fundOwnership',
   'majorDirectHolders',
   'majorHoldersBreakdown',
   'insiderTransactions',
   'insiderHolders',
   'netSharePurchaseActivity',
   'earnings',
   'earningsHistory',
   'earningsTrend',
   'industryTrend',
   'indexTrend',
   'sectorTrend' ]





```{r}

aapl_income_json <- read_json("https://query2.finance.yahoo.com/v10/finance/quoteSummary/AAPL?modules=incomeStatementHistory")
```

```{r}
aapl_income_json$quoteSummary$result[[1]]$incomeStatementHistory$incomeStatementHistory[1] %>% 
  unlist %>% 
  enframe %>% 
  pivot_wider(names_from = name, values_from = value)
```

```{r}
getIncome("FB", format="raw")
```






```{r}

getIncomeJSON <- function (ticker, report="yearly") {
  url <- paste0("https://query2.finance.yahoo.com/v10/finance/quoteSummary/",ticker,"?modules=incomeStatementHistory")
  url_q <- paste0("https://query2.finance.yahoo.com/v10/finance/quoteSummary/",ticker,"?modules=incomeStatementHistoryQuarterly")
  
  ifelse(report=="yearly" | report=="y", df <- read_json(url), 
         ifelse(report=="quarterly" | report=="q", df <- read_json(url_q),
                stop('Report type can only be "yearly", "y", "quarterly" or "q".')))
  l <- list()
  
  for (i in 1:length(df$quoteSummary$result[[1]]$incomeStatementHistory$incomeStatementHistory)) {
    l[[i]] <- df$quoteSummary$result[[1]]$incomeStatementHistory$incomeStatementHistory[i] %>% 
    unlist %>% 
    enframe %>% 
    pivot_wider(names_from = name, values_from = value)
  }
  df <- bind_rows(l) %>% 
    select(endDate.fmt,ends_with(".raw"), -endDate.raw)
  
  df <- df %>% dplyr::transmute(
    date = parse_date(endDate.fmt, format ="%Y-%m-%d"),
    revenue = parse_number(totalRevenue.raw),
    cost_revenue= parse_number(costOfRevenue.raw),
    gross_profit = parse_number(grossProfit.raw),
    rd = parse_number(researchDevelopment.raw),
    sga = parse_number(sellingGeneralAdministrative.raw),
    operating_expenses = parse_number(totalOperatingExpenses.raw),
    operating_income = parse_number(operatingIncome.raw),
    other_income = parse_number(totalOtherIncomeExpenseNet.raw),
    ebit = parse_number(ebit.raw),
    interest_expense = parse_number(interestExpense.raw),
    ebt = parse_number(incomeBeforeTax.raw),
    tax = parse_number(incomeTaxExpense.raw),
    ni_operations = parse_number(netIncomeFromContinuingOps.raw),
    ni = parse_number(netIncome.raw),
    ni_to_shareholders = parse_number(netIncomeApplicableToCommonShares.raw)
  )
  
  df <- df %>% 
    mutate(
      ticker = toupper(ticker),
      year = as.integer(format(date, "%Y")),
      report = ifelse(report=="yearly" | report=="y", "yearly","quarterly")
    ) %>% 
    select (ticker, year, date, report, everything())
  
  return(df)
   
}


```






```{r}
#getIncomeJSON2

json <- fromJSON("https://query2.finance.yahoo.com/v10/finance/quoteSummary/AAPL?modules=cashflowStatementHistoryQuarterly")

df_json <- as_tibble(json, validate = F) 

df_json1 <- flatten(df_json[[1]][[1]][[1]][[1,1]])
```




```{r}
list_json <- map_if(json, is.data.frame, list) 

df_json_list <- flatten(as_tibble(list_json))

df_json_list1 <- flatten(df_json_list[[1]][[1]][[1]][[1,1]])
```


```{r}
test1 <- fromJSON("https://query2.finance.yahoo.com/v10/finance/quoteSummary/AAPL?modules=incomeStatementHistory")

df_test151 <- flatten(test1[[1]][[1]][[1]][[1,1]])

```



```{r}
json2tidy <- function (url) {
  json <- fromJSON(url)
  df <- flatten(json[[1]][[1]][[1]][[1,1]])
  return(df)
} 
```


Yahoo Finance Modules:
modules = [
   'assetProfile',
   'incomeStatementHistory',
   'incomeStatementHistoryQuarterly',
   'balanceSheetHistory',
   'balanceSheetHistoryQuarterly',
   'cashflowStatementHistory',
   'cashflowStatementHistoryQuarterly',
   'defaultKeyStatistics',
   'financialData',
   'calendarEvents',
   'secFilings',
   'recommendationTrend',
   'upgradeDowngradeHistory',
   'institutionOwnership',
   'fundOwnership',
   'majorDirectHolders',
   'majorHoldersBreakdown',
   'insiderTransactions',
   'insiderHolders',
   'netSharePurchaseActivity',
   'earnings',
   'earningsHistory',
   'earningsTrend',
   'industryTrend',
   'indexTrend',
   'sectorTrend' ]


```{r}
t<- json2tidy("https://query2.finance.yahoo.com/v10/finance/quoteSummary/AAPL?modules=cashflowStatementHistory")

t <- t %>% 
  select(endDate.fmt, ends_with(".raw"), -endDate.raw)

names(t) <- sub(".raw","", names(t))
names(t) <- sub(".fmt","", names(t))
```



```{r}
getFinancials2 <- function (ticker, report_type="annual") {
  ticker <- base::toupper(ticker)
  json2tidy <- function (url) {
    json <- fromJSON(url)
    df <- flatten(json[[1]][[1]][[1]][[1,1]])
    return(df)
  } 
  baseURL <- "https://query2.finance.yahoo.com/v10/finance/quoteSummary/"
  cfURL <- ifelse(report_type=="quarterly",
                      paste0(baseURL, ticker, "?modules=", "cashflowStatementHistoryQuarterly"),
                      paste0(baseURL, ticker, "?modules=", "cashflowStatementHistory"))
  
  json2tidy <- function (url) {
  json <- fromJSON(url)
  df <- flatten(json[[1]][[1]][[1]][[1,1]])
  return(df)
  }
  
  getIncome <- function(ticker, report_type="annual") {
    baseURL <- "https://query2.finance.yahoo.com/v10/finance/quoteSummary/"
    incomeURL <- ifelse(report_type=="quarterly",
                      paste0(baseURL, ticker, "?modules=", "incomeStatementHistoryQuarterly"),
                      paste0(baseURL, ticker, "?modules=", "incomeStatementHistory"))
    df <- json2tidy(incomeURL) %>% 
      select(endDate.fmt, ends_with(".raw"), -endDate.raw)
    names(df) <- sub(".raw","", names(df))
    names(df) <- sub(".fmt","", names(df))
    df$ticker <- ticker
    return(df)
  }
  
  getBS <- function(ticker, report_type="annual") {
   baseURL <- "https://query2.finance.yahoo.com/v10/finance/quoteSummary/"
   bsURL <- ifelse(report_type=="quarterly",
                      paste0(baseURL, ticker, "?modules=", "balanceSheetHistoryQuarterly"),
                      paste0(baseURL, ticker, "?modules=", "balanceSheetHistory"))
    df <- json2tidy(bsURL) %>% 
      select(endDate.fmt, ends_with(".raw"), -endDate.raw)
    names(df) <- sub(".raw","", names(df))
    names(df) <- sub(".fmt","", names(df))
    df$ticker <- ticker
    return(df)
  }
  
  getCF <- function(ticker, report_type="annual") {
    baseURL <- "https://query2.finance.yahoo.com/v10/finance/quoteSummary/"
    cfURL <- ifelse(report_type=="quarterly",
                      paste0(baseURL, ticker, "?modules=", "cashflowStatementHistoryQuarterly"),
                      paste0(baseURL, ticker, "?modules=", "cashflowStatementHistory"))
    
    df <- json2tidy(cfURL) %>% 
      select(endDate.fmt, ends_with(".raw"), -endDate.raw)
    names(df) <- sub(".raw","", names(df))
    names(df) <- sub(".fmt","", names(df))
    df$ticker <- ticker
    return(df)
  } 
  
  m <- list()
  for (i in ticker) {
    l <- list()
    l[[1]] <- getIncome(i)
    l[[2]] <- getBS(i)
    l[[3]] <- getCF(i)
    m[[match(i, ticker)]] <- purrr::reduce(l, full_join, by = c("ticker", "endDate")) %>% 
      dplyr::select(ticker, endDate, everything(), -netIncome.y) %>%
      dplyr::rename(netIncome = netIncome.x)
  }
  
  result <- dplyr::bind_rows(m)
  options(scipen = 999)
  return(result)
}  
```

```{r}

```


```{r}
bruh <- getFinancials2()
```

```{r}
getIncome("AAPL")
```



```{r}

brk.b <- read_json('https://query2.finance.yahoo.com/v10/finance/quoteSummary/BRK.B?modules=incomeStatementHistory')

fb <- read_json('https://query2.finance.yahoo.com/v10/finance/quoteSummary/FB?modules=incomeStatementHistory')


length(brk.b$quoteSummary$result[[1]]$incomeStatementHistory$incomeStatementHistory)
```



```{r}

tickers = c("FB","GOOG")

list <- lapply(X=ticker, FUN=getIncomeJSON)

assign(income_statements, bind_rows(list), envir=.GlobalEnv)

  
```


```{r}

getIncomeV2 <- function (ticker, report="yearly") {
  
  
  getIncomeJSON <- function (ticker, report) {
  url <- paste0("https://query2.finance.yahoo.com/v10/finance/quoteSummary/",ticker,"?modules=incomeStatementHistory")
  url_q <- paste0("https://query2.finance.yahoo.com/v10/finance/quoteSummary/",ticker,"?modules=incomeStatementHistoryQuarterly")
  
  ifelse(report=="yearly" | report=="y", df <- read_json(url), 
         ifelse(report=="quarterly" | report=="q", df <- read_json(url_q),
                stop('Report type can only be "yearly", "y", "quarterly" or "q".')))
  
  
  l <- list()
  
  ifelse(
    length(df$quoteSummary$result[[1]]$incomeStatementHistory$incomeStatementHistory)!=0,
    {for (i in 1:length(df$quoteSummary$result[[1]]$incomeStatementHistory$incomeStatementHistory)) {
      l[[i]] <- df$quoteSummary$result[[1]]$incomeStatementHistory$incomeStatementHistory[i] %>% 
      unlist %>% 
      enframe %>% 
      pivot_wider(names_from = name, values_from = value)}
    df <- bind_rows(l) 
      }, df <- tibble(ticker))
  
  
  
  ifelse("endDate.fmt" %in% colnames(df),
         df <- df %>%  mutate(date = parse_date(endDate.fmt, format ="%Y-%m-%d")),
         df <- df %>%  mutate(date=NA))
  
  ifelse("totalRevenue.raw" %in% colnames(df),
         df <- df %>% mutate(revenue = parse_number(totalRevenue.raw)),
         df <- df %>% mutate(revenue=NA))
  
  ifelse("costOfRevenue.raw" %in% colnames(df),
         df <- df %>% mutate(cost_revenue= parse_number(costOfRevenue.raw)),
         df <- df %>% mutate(cost_revenue=NA))
  
  ifelse("grossProfit.raw" %in% colnames(df),
         df <- df %>% mutate(gross_profit = parse_number(grossProfit.raw)),
         df <- df %>% mutate(gross_profit=NA))
  
  ifelse("researchDevelopment.raw" %in% colnames(df),
         df <- df %>% mutate(rd = parse_number(researchDevelopment.raw)),
         df <- df %>%  mutate(rd=NA))
  
  ifelse("sellingGeneralAdministrative.raw" %in% colnames(df),
         df <- df %>% mutate(sga = parse_number(sellingGeneralAdministrative.raw)),
         df <- df %>% mutate(sga=NA))
  
  ifelse("totalOperatingExpenses.raw" %in% colnames(df),
         df <- df %>% mutate(operating_expenses = parse_number(totalOperatingExpenses.raw)),
         df <- df %>% mutate(operating_expenses=NA))
  
  ifelse("operatingIncome.raw" %in% colnames(df),
         df <- df %>% mutate(operating_income = parse_number(operatingIncome.raw)),
         df <- df %>% mutate(operating_income = NA))
  
  ifelse("totalOtherIncomeExpenseNet.raw" %in% colnames(df),
         df <- df %>% mutate(other_income = parse_number(totalOtherIncomeExpenseNet.raw)),
         df <- df %>% mutate(other_income=NA))
  
  ifelse("ebit.raw" %in% colnames(df),
         df <- df %>% mutate(ebit = parse_number(ebit.raw)),
         df <- df %>% mutate(ebit = NA))
  
  ifelse("interestExpense.raw" %in% colnames(df),
         df <- df %>% mutate(interest_expense = parse_number(interestExpense.raw)),
         df <- df %>% mutate(interest_expense = NA))
  
  ifelse("incomeBeforeTax.raw" %in% colnames(df),
         df <- df %>% mutate(ebt = parse_number(incomeBeforeTax.raw)),
         df <- df %>% mutate(ebt = NA))
  
  ifelse("incomeTaxExpense.raw" %in% colnames(df),
         df <- df %>% mutate(tax = parse_number(incomeTaxExpense.raw)),
         df <- df %>% mutate(tax = NA))
  
  ifelse("netIncomeFromContinuingOps.raw" %in% colnames(df),
         df <- df %>% mutate(ni_operations = parse_number(netIncomeFromContinuingOps.raw)),
         df <- df %>% mutate(ni_operations = NA))
  
  ifelse("netIncome.raw" %in% colnames(df),
         df <- df %>% mutate(ni = parse_number(netIncome.raw)),
         df <- df %>% mutate(ni = NA))
  
  ifelse("netIncomeApplicableToCommonShares.raw" %in% colnames(df),
         df <- df %>% mutate(ni_to_shareholders = parse_number(netIncomeApplicableToCommonShares.raw)),
         df <- df %>% mutate(ni_to_shareholders = NA))
  
  ifelse("netIncomeApplicableToCommonShares.raw" %in% colnames(df),
         df <- df %>% mutate(maxAge = NA),
         df <- df %>% mutate(maxAge = NA))
  
  df <- df %>% 
    select(-ends_with(".raw"), -ends_with(".fmt"), -ends_with(".longFmt"),)

  df <- df %>% 
    mutate(
      ticker = toupper(ticker),
      #year = ifelse(length(df$date)!=0, as.integer(format(date, "%Y")), NA),
      report = ifelse(report=="yearly" | report=="y", "yearly","quarterly")
    ) %>% 
    select (ticker, date, report, -maxAge, everything())
  
  Sys.sleep(5)
  return(df)
  } 
  
  
  list <- lapply(X=ticker, FUN=getIncomeJSON, report=report)

  assign("income_statements", bind_rows(list), envir=.GlobalEnv)
  
}
```




```{r}
companies=c("FB", "GOOG")

getIncomeMultiple <- function (tickers) {
  list <- lapply(X=tickers, FUN=getIncome)
  assign("income_statements", bind_rows(list), envir=.GlobalEnv)
  
}

getIncomeMultiple(sp500$symbol[1:50])

  
```




```{r}
income_statements %>% 
  dplyr::filter(year=="2018") %>% 
  transmute(
    ticker=ticker,
    ebit_margin=ebit/revenue,
    `r&d_percentage_expenses` = `r&d`/operating_expenses
  )
```


```{r}
getFinancials("GOOG", format="raw")
```



```{r}
getIncomeMultiple(c("MSFT", "AAPL"))
```












































